Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-11 WSSSPE2_report/WSSSPE2_review.tex
change to use macro

The enablers of and barriers to software sustainability, roughly ranked by attendee votes are shown in Tables~\ref{tb:software_sustainability_enablers} and \ref{tb:software_sustainability_barriers}, respectively.\footnote{A few other items were suggested as barriers, but were not voted on due to lack of time in the session:
layering up dependencies;
using software past its sustainable life;
using software past its usable life;
inertia for accepted answers vs wrong/right answers;
monolithic or poor code; and
need to restructure code when hardware/software/libraries change.
}

>>>>

The enablers of and barriers to software sustainability, roughly ranked by attendee votes are shown in {\tablename}s~\ref{tb:software_sustainability_enablers} and \ref{tb:software_sustainability_barriers}, respectively.\footnote{A few other items were suggested as barriers, but were not voted on due to lack of time in the session:
layering up dependencies;
using software past its sustainable life;
using software past its usable life;
inertia for accepted answers vs wrong/right answers;
monolithic or poor code; and
need to restructure code when hardware/software/libraries change.
}
